\documentclass[10pt,a4paper]{moderncv}

% moderncv themes
\moderncvtheme[blue]{classic}

% adjust the page margins
\usepackage[scale=0.8]{geometry}

% personal data
\firstname{TERRY}
\familyname{TAO}
\mobile{Mobile: 18217618487}
\email{Email: 78019092@qq.com}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{BASIC INFO.}
\cvdoubleitem{Gender}{Male}{Degree}{Master's}
\cvdoubleitem{Major}{Computer Sciences}{Experience}{8 years}

\section{SELF ASSESSMENT}
\cvlistitem{Expert in JAVA and related technologies, have strong analyzing and problem solving skills.}
\cvlistitem{Three years software developing experience in American companies, able to communicate fluently in English.}
\cvlistitem{Familiar with Test Driven Development and Agile Development, and familiar with development and releasing process of large software systems.}
\cvlistitem{Familiar with project management process, have some experience of managing projects, and have good communication skills.}


\section{WORK EXPERIENCE}

\cventry{2013.4--present}{Technical Lead}{DataYes}{}{}{
  Responsible for the architecture design of Portfolio Management System, and lead the team in development.
  \begin{itemize}
  \item Design system architecture based on Java, Scala, Play Framework and Javascript, with Restful interface between backend and frontend.
  \item Communicate with invest team, collect the requirements and provide support.
  \item Design a flexible database schema, to support various financial instruments and business types.
  \item Design and implement a privilege system based on Spring Security
  \item Coordinate the team with other teams.
  \item Tune the performance of the application from aspects of database and JVM etc.
\end{itemize}}

\cventry{2012.6--2013.4}{Senior Software Engineer/Architect}{i-MD.com}{}{}{
  Lead the team to develop the web site backend. Collect and analyze the user data. Maintain the production and QA environments.
  \begin{itemize}
  \item Build the user data tracking system, and analyze the user data.
  \item Design and implement the new user system, and migrate from the old system.
  \item Design and implement the user infomation interface for an outsourced website.
\end{itemize}}

\cventry{2011.5--2012.6}{Senior Software Engineer}{iSoftstone}{}{}{
  Working in Morgan Stanley IT department. Responsible for design,
  implement and maitain Intrest Rate Derivative yield curve
  services. Provide data and support to traders, strats and other
  teams in IT department.
  \begin{itemize}
  \item Communicate with traders, strats and other team, gether their
    requirements.
  \item Design and implement the intraday marking to market system, and perform testing.
  \item Working on the Fixed Income department's next generate risk system.
\end{itemize}}

\cventry{2009.01--2011.4 (Overseas)}{Applications
  Developer}{Oracle}{}{}{ Responsible the development of the main
  products (P6 Web Services, P6 Web Access and Integration API), and
  participate in the team's management. Analyze the users'
  requirements, design and implement new features, maintain existing
  functionality and fix bugs. Improve products' performance to fit
  enterprise-level deployment. Released major release 8.0, and
  released several service packs and hotfixes.}

\cventry{2008.3--2008.12 (Overseas)}{Programmer, Intern}{Primavera System Inc}{}{}{
  Participated in the development and testing of the products, helped other developers to develop features and release products.}

\section{EDUCATION}
\cventry{2006.8--2008.12 (Overseas)}{Master's, Computing Sciences}{Villanova University}{Philadelphia, PA}{\textit{GPA: 3.8/4.0}}{\hfill\newline
  Got full scholarship from the school. Helped professors with their research as Research Asistant (RA).\newline
  Participated in the research of XMPP protocol, and created a model of XMPP protocol with CPN Tools.\newline
  The topic of independent study is Robot Localization using Particle Filter.\newline}
\cventry{2002.9--2006.7}{Bachelor's, Computer Sciences and Technologies}{Beijing University of Posts and Telecommunications}{Beijing}{}{\hfill\newline
  Ranked top 5\% in the department. Got scholarship several times because of outstanding academic performance.\newline
  The topic of curriculum design is The monitoring system based on embedded Linux, and got Outstanding Curriculum Design Award.\newline}

\section{LANGUAGE}
\cvlanguage{English}{Excellent}{Have been studied and working in the USA for about 5 years, able to communicate fluently in English, orally and in written.}


\end{document}
