\documentclass[10pt,a4paper]{moderncv}

% moderncv themes
\moderncvtheme[blue]{classic}

% adjust the page margins
\usepackage[scale=0.85]{geometry}

% personal data
\firstname{TAO}
\familyname{TAO}
\mobile{Mobile: (+86) 18217618487}
\email{Email: 78019092@qq.com}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{BASIC INFO}
\cvdoubleitem{Gender}{Male}{Degree}{Master's}
\cvdoubleitem{Major}{Computer Sciences}{Experience}{10 years}

\section{SELF ASSESSMENT}
\cvlistitem{Solid knowledge and experience in Computer Science and software development.}
\cvlistitem{In depth knowledge of system design and object-oriented development.}
\cvlistitem{Familiar with Test Driven Development, Agile and Scrum.}
\cvlistitem{Fluent English communication in spoken and written.}

\section{TECHNICAL SKILLS}

\cvitem{Advanced}{\textsc{Java}, \textsc{Linux}, \textsc{OOD}, \textsc{MySQL}, \textsc{Git}}
\cvitem{Intermediate}{\textsc{C++}, \textsc{Qt}, \textsc{Python}, \textsc{HTML}, \textsc{Javascript}, \textsc{CSS}, \textsc{NodeJS}}
\cvitem{Basic}{C\#, \textsc{OpenCV}}

\section{EXPERIENCE}

\cventry{2016.5--present}{Software Technical Lead}{Digitech, Inc.}{}{}{
  \begin{itemize}
  \item Lead software development and responsible for software architecture design.
  \item Designed and implemented the following projects in C++/QT.
  \begin{itemize}
    \item Software for array-antenna UAV detection system.
    \item Spectrum analyzer software based on Signal hound BB60C API.
    \item Signal generator software based on Signal hound VSG25A API.
  \end{itemize}
  \item Location tracking system based on GPS/BD module in NodeJS.
\end{itemize}}

\cventry{2013.4--2016.4}{Senior Software Engineer}{DataYes, Inc.}{}{}{
  Responsible for the architecture design of Portfolio Management System.
  \begin{itemize}
  \item Designed system architecture based on Java technologies.
  \item Implemented core functinalities of the system.
  \item Communicate requirements with invest team, and coordinate with other teams.
\end{itemize}}

\cventry{2012.6--2013.4}{Software Engineer}{i-MD.com}{}{}{
  \begin{itemize}
  \item Developed the web site backend in Java and MongoDB.
  \item Designed and implemented the user data tracking system.
\end{itemize}}

\cventry{2011.5--2012.6}{Software Engineer}{iSoftstone}{}{}{
  \begin{itemize}
  \item Worked in Morgan Stanley IT department.
  \item Designed, implemented and maintained Interest Rate Derivative yield curve services.
  \item Worked on the Fixed Income department's next generation risk system.
\end{itemize}}

\cventry{2008.12--2011.4}{Applications
  Developer}{Oracle}{}{}{ Development of Web Services and API for the company's project management product.}

\section{EDUCATION}
\cventry{2006.8--2008.12}{Master's, Computing Sciences}{Villanova University}{Philadelphia, PA}{\textit{GPA: 3.8/4.0}}{}
\cventry{2002.9--2006.7}{Bachelor's, Computer Sciences and Technologies}{Beijing University of Posts and Telecommunications}{Beijing}{}{}

\end{document}
