\documentclass[10pt,a4paper]{moderncv}

% moderncv themes
\moderncvtheme[blue]{classic}

% adjust the page margins
\usepackage[scale=0.8]{geometry}

% personal data
\firstname{TERRY}
\familyname{TAO}
\mobile{Mobile: 18217618487}
\email{Email: librakevin@gmail.com}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{BASIC INFO.}
\cvdoubleitem{Gender}{Male}{Degree}{Master's}
\cvdoubleitem{Major}{Computer Sciences}{Experience}{6 years}

\section{SELF ASSESSMENT}
\cvlistitem{Expert in JAVA and related technologies, have strong analyzing and problem solving skills.}
\cvlistitem{Got Master's degree from an American university, and have three years software developing experience in an American company, able to communicate fluently in English.}
\cvlistitem{Familiar with Test Driven Development and Agile Development, and familiar with development and releasing process of large software systems.}
\cvlistitem{Familiar with project management process, have some experience of managing projects, and have good communication skills.}


\section{WORK EXPERIENCE}

\cventry{2013.4--present}{Technical Lead}{DataYes}{}{}{
  Responsible for the architecture design of Portfolio Management System, and lead the team in development.
  \newline
  \begin{itemize}
  \item Design the architecture based on Java, Scala, Play Framework and Javascript, using Restful interface between backend and frontend.
  \item Communicate with invest team, collect the requirements and provide support.
  \item Design a flexible database schema, to support various financial instruments and business types.
  \item Design and implement a privilege system based on Spring Security
  \item Coordinate the team with other teams.
\end{itemize}}

\cventry{2012.6--2013.4}{Senior Software Engineer/Architect}{i-MD.com}{}{}{
  Lead the team to develop the web site backend. Collect and analyze the user data. Maintain the production and QA environments.
  \newline
  \begin{itemize}
  \item Build the user data tracking system, and analyze the user data.
  \item Design and implement the new user system, and migrate from the old system.
  \item Design and implement the user infomation interface for an outsourced website.
\end{itemize}}

\cventry{2011.5--2012.6}{Senior Software Engineer}{iSoftstone}{}{}{
  Working in Morgan Stanley IT department. Responsible for design,
  implement and maitain Intrest Rate Derivative yield curve
  services. Provide data and support to traders, strats and other
  teams in IT department.
  \newline
  \begin{itemize}
  \item Communicate with traders, strats and other team, gether their
    requirements.
  \item Design and implement the intraday marking to market system, and perform testing.
  \item Working on the Fixed Income department's next generate risk system.
\end{itemize}}

\cventry{2010.3--2011.4 (Overseas)}{Applications
  Developer}{Oracle}{}{}{ Responsible the development of the main
  products (P6 Web Services, P6 Web Access and Integration API), and
  participate in the team's management. Analyze the users'
  requirements, design and implement new features, maintain existing
  functionality and fix bugs. Improve products' performance to fit
  enterprise-level deployment. Released major release 8.0, and
  released several service packs and hotfixes.
  \newline
  \begin{itemize}
  \item Improved the products' performance by finding the bottleneck and optimizing the code.
    \begin{itemize}
    \item Monitored the SQL queries to the database, found and optimized the queries with performance hit.
    \item Optimized the user interface (Swing), improved the user experience.
    \item Optimized the XML-generation code in eventing subsystem.
    \end{itemize}
  \item Led the development of eventing mechanism for P6 products.
    \begin{itemize}
    \item Designed the eventing mechanism based on JMS 1.1.
    \item Designed the code infra-structure for eventing.
    \item Implemented automated testing tools for integrated testing eventing mechanism.
    \item Mentored testers for writing testing scripts.
    \end{itemize}
  \item Was in the position of scrum master, and helped project manager to manage the projects and the team. My responsibilities were:
    \begin{itemize}
    \item Plan and schedule tasks before each sprint.
    \item Call meetings for everyday's scrum, check the status of the projects and discuss any problems or hurdles.
    \item Make sure every feature is covered by automatic or manual tests, to ensure the quality of the products.
    \item Call health check meeting in the middle of the sprints, reschedule or shuffle the tasks if necessary.
    \item Make report at the sprint review meeting in the company.
    \end{itemize}
  \item Released 5 versions of different products within 1 month.
    \begin{itemize}
    \item Managed to finish tasks in high tensity, and ensured the quality of the products.
    \item Performed integrated tests, regression tests and checklist for the products.
    \end{itemize}
\end{itemize}}

\cventry{2009.1--2010.2 (Overseas)}{Associate Applications Developer}{Oracle}{}{}{
  Responsible for the development of the main products, add new features, maintain existing functionality, and fix bugs. Released the major version 7.0 of the products, and several other versions.
  \newline
  \begin{itemize}
  \item Participated in the development of Contract Management Web Services.
    \begin{itemize}
    \item Designed the architecture of the product (based on the backend of existing product, use Apache CXF as the frontend for web services, and use code generation extensively to automatically generate production code).
    \item Implemented code generation tools with Groovy, and introduced Groovy to the other developers in the company.
    \item Analyzed and debugged existing backend code (EJB), and modified the backend code to fit web services' requirement.
    \end{itemize}
  \item Created installers for the main products using Oracle Universal Installer.
  \item Implemented the Feature Request workflow with Oracle BPM 11g and P6 Web Services. The workflow was deployed in the company and used by the development teams.
\end{itemize}}

\cventry{2008.3--2008.12 (Overseas)}{Programmer, Intern}{Primavera System Inc}{}{}{
  Participated in the development and testing of the products, helped other developers to develop features and release products.
  \newline
  \begin{itemize}
  \item Migrate the web service framework from Axis2 to Apache CXF, and got to deeply understand web services.
  \item Implemented XML exporter/importer using StAX API, and got familiar with business logic of P6 project management software.
  \item Created Java and C\# demos for P6 Web Services.
\end{itemize}}

\section{EDUCATION}
\cventry{2006.8--2008.12 (Overseas)}{Master's, Computing Sciences}{Villanova University}{Philadelphia, PA}{\textit{GPA: 3.8/4.0}}{\hfill\newline
  Got full scholarship from the school. Helped professors with their research as Research Asistant (RA).\newline
  Participated in the research of XMPP protocol, and created a model of XMPP protocol with CPN Tools.\newline
  The topic of independent study is Robot Localization using Particle Filter.\newline}
\cventry{2002.9--2006.7}{Bachelor's, Computer Sciences and Technologies}{Beijing University of Posts and Telecommunications}{Beijing}{}{\hfill\newline
  Ranked top 5\% in the department. Got scholarship several times because of outstanding academic performance.\newline
  The topic of curriculum design is The monitoring system based on embedded Linux, and got Outstanding Curriculum Design Award.\newline}

\section{LANGUAGE}
\cvlanguage{English}{Excellent}{Have been studied and working in the USA for about 5 years, able to communicate fluently in English, orally and in written.}


\end{document}
